Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
update on the CL part

% Packages for bold math
\usepackage{bm}
\newcommand{\mathbold}[1]{\bm{#1}}
\newcommand{\mbf}[1]{\mathbf{#1}}
\renewcommand{\mid}{\,|\,}

@@

% CL section
\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previous learnt functions. 
The approaches proposed in the CL literature can be categorized into inference-based, reharsal-based, and model-based methods, we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews. The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\cite{kirkpatrick2017overcoming}, SI~\cite{zenke17a}), or VCL~\cite{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
However, encoding functional knowledge in the weights does not guarantees a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}. These methods bridge the gap between objective and reharsal-based methods, since they rely on a subset of the training data for each task to compute the regularization term. Recent methods, such as DER~\cite{buzzega2020dark}, FROMP~\cite{pan2020continual}, and S-FSVI~\cite{rudner2022continual} achieve state-of-the-art performances among the objective-based techniques in several CL benchmarks. 
% It should be written clearly that our method actually is doing a "functional" reharsal, because we store a set of inducing points that are replayed in order to check if the logits change.

@@

In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
%
\begin{equation} \label{eq-empirical-risk}
  \weights^{*} = 
  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
\end{equation}
%
If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.

@@

\textbf{Uncertainty quantification} \todo{Move this section to the related work}
Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) p(\weights)}$ as
it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.

@@

\textbf{Linearization gives rise to a Gaussian process}
Our goal is to build a sparse function-space representation of a neural network.
Gaussian processes $f$ are an extension of the multivariate normal that characterizes a distribution over
functions in terms of the first two moments.
They are defined by a mean function $\mu(\cdot)$ and a covariance (aka kernel) function $\kappa(\cdot,\cdot)$.
Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space
lead to function space equivalent approximations.
As Gaussian distributions remain tractable under linear transformations, a linear function in
terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
f_\weights(\vx) \approx 
%g_\weights(\mathbf{x}) = 
\phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx')
\end{equation}
% The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$
with the GGN.
Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
%g_{\weights}(\vx) = 
\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$.
\todo{do we need this sentence about the Hessian to get Laplace-GGN??}
Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by,
\begin{equation} 
\label{eq-laplace-approx-function-space}
% g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
  \mu(\vx) =  0 \quad \text{and} \quad
  \kappa(\vx, \vx')
  = \frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}, 
\end{equation}
where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}). In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extend for the multi-dimensional case. With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$. \citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data. Similarly, \citet{immer2021improving} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model. Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$. In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments. We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.

\section{\our: Sparse function-space represenation of neural networks}
\paragraph{GP in the dual parameters}
As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ found through the Bayesian update equation using  GP prior and likelihood function can be parameterized by $\valpha$ and $\vbeta$:
\begin{equation}  \label{eq:gp_pred}
 \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
\end{equation}
%
The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods. In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior. At the same time, in \cite{adam2021dual, chang2020fast}, they showed this relationship for variational Gaussian processes where the above expectation is with respect to the approximate posterior from the variational approximation. The parameter $\alpha$ relates to non-Bayesian approaches, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. For more detail, see \citet{wilkinson2023bayes}, which shows the links between approximate inference methods and how they solve the \cref{eq:dual_param}.

\paragraph{Dual parameters from NN}
Given we are making a Laplace approximation of the neural network we can remove the expectation over the posterior to find the following approximate dual variables (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation). Meaning we arrive at the following dual variables.
\begin{equation}
\label{eq:dual_param_laplace}
\hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad \text{and} \quad
\hat{\beta}_i \coloneqq - \nabla^2_{f_i f_i}\log p(y_i \mid f_i).
\end{equation}

@@

\paragraph{Sparsifying the NNGP}
\label{sec:sparse-dual-gp}
%
Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation. Many sparsifying approaches exist, we refer the reader to \cite{quinonero2005unifying} for an overview. Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation. We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC approximaton \cite{quinonero2005unifying}, which is to define the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$. Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.

As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}. In the paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients. In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form. 
%
\begin{equation} 
	\valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
	\vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
\label{eq:dual_sparse}
\end{equation}
the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$. Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
\begin{equation}\label{eq:dual_sparse_post}
   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
\end{equation}
where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$. The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$. Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.  Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel. Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset. It is important to highlight that the sparsifying approach is independent of the approximate inference technique. The \cref{eq:dual_param} are determined from the neural network. More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.

\section{Sparse function-space sequential learning}

@@

\subsection{Sparse functional regularization (SFR) in continual learning}
% Definition of CL -> a sequence of tasks 
% Possible storyline:
after each task we use the model

In this paper we consider the Continual learning setting were a sequence of disjoint sets

\begin{equation}
 	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, \quad \forall s \in [1, t-1]
 \end{equation}

\begin{equation}
	\mathcal{R}_\textit{SFR}(\weights) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right]
\end{equation} 
with $f_\vw(\MZ_{s}), f_{\vw_s}(\MZ_s) \in \R^m$ are vectors of the outputs of the neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$.

%\begin{equation}
%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
%\end{equation}

\begin{equation}
	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
\end{equation}

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	%\input{tables/img_super.tex}
\end{table}

Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks. After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}. We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.

@@

\section{Discussion and conclusion}
\label{sec:conclusion}
%

@@

\phantomsection%
\addcontentsline{toc}{section}{References}
\begingroup
\small
\bibliographystyle{abbrvnat}
\bibliography{bibliography}%zotero-library
\endgroup

@@

This supplementary document is organized as follows. 
%
\cref{app:method} provides a more extensive overview of the techncical details of \our.
%
\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
%
\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
%
\cref{app:experiments} provides the full details of each individual experiments in the main paper.

\section{Method details}
\label{app:method}
%
Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

\section{Sparse functional regularisation in continual learning}
\label{app:cl}

\subsection{Extending the CL regularizer to multi-class settings}
\begin{equation}
	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
\end{equation}

\section{Sparse functional model-based reinforcement learning}
\label{app:rl}

>>>>

% Packages for bold math
\usepackage{bm}
\newcommand{\mathbold}[1]{\bm{#1}}
\newcommand{\mbf}[1]{\mathbf{#1}}

@@

% CL section
\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution, which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previously learnt functions. 
The approaches proposed in the CL literature can be categorized into inference-based, rehearsal-based, and model-based methods; we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews. The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
However, encoding functional knowledge in the weights does not guarantee a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}. These methods bridge the gap between objective and rehearsal-based methods since they rely on a subset of the training data for each task to compute the regularization term. Recently proposed methods, such as DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performances among the objective-based techniques in several CL benchmarks.

% It should be written clearly that our method actually is doing a "functional" reharsal, because we store a set of inducing points that are replayed in order to check if the logits change.

@@

In supervised learning, given a data set $\dataset = \dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
%
\begin{equation} \label{eq-empirical-risk}
  \weights^{*} = 
  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
\end{equation}
%
If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.

@@

\textbf{Uncertainty quantification}
Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) p(\weights)}$ as
it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.

@@

\textbf{Linearization gives rise to a Gaussian process}
Our goal is to build a sparse function-space representation of a neural network.
Gaussian processes $f$ are an extension of the multivariate normal that characterizes a distribution over
functions in terms of the first two moments.
They are defined by a mean function $\mu(\cdot)$ and a covariance (aka kernel) function $\kappa(\cdot,\cdot)$.
Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space
lead to function space equivalent approximations.
As Gaussian distributions remain tractable under linear transformations, a linear function in
terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
f_\weights(\vx) \approx 
%g_\weights(\mathbf{x}) = 
\phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx')
\end{equation}
% The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$
with the GGN.
Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
%g_{\weights}(\vx) = 
\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$.
\todo{do we need this sentence about the Hessian to get Laplace-GGN??}
Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by,
\begin{equation} 
\label{eq-laplace-approx-function-space}
% g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
  \mu(\vx) =  0 \quad \text{and} \quad
  \kappa(\vx, \vx')
  = \frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}, 
\end{equation}
where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}). In \cref{eq-laplace-approx-function-space} and \cref{eq:weight_func}, for notational convenience, we restricted the function output to single dimension, but this could be easily extend for the multi-dimensional case. With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$. \citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data. Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model. Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$. In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments. We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.

\section{\our: Sparse function-space represenation of neural networks}
\paragraph{Linearization in the dual parameters}
As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
\begin{equation}  \label{eq:gp_pred}
 \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
\end{equation}\todo{ More explination of the dual equation 6 the loss landscape link. Perbutation point linked directly to that here. }
%
The parameters $(\alpha_i, \beta_i)$ are the dual parameters that arise in the dual formulations used in, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. The above relations holds for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. The question is how do we form the dual variables without access to the exact posterior and different approximate inference techniques solve the question in different ways. Bound techniques such as \citet{jaakkola1997variational} attempt to bound the integral thus making the integral tractable, while Expecation Propogation (EP) as used in \citet{csato2002sparse} iteratively finds dual variables but sets them to log of the expectation of the approximate posterior. Meanwhile variational inference  \cite{khan2017conjugate, adam2021dual} find them using the variational approximation of the posterior to solve the integral.

\paragraph{Neural network dual variables}
As we are using the MAP solution of the neural network loss, we will use the Laplace approximation for the dual variables but other techniques could be used. As detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian}, the dual variables of the Laplace approximation are the same as removing the posterior averaging from \cref{eq:dual_param}, meaning:
\begin{equation}
\label{eq:dual_param_laplace}
\hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad \text{and} \quad
\hat{\beta}_i \coloneqq - \nabla^2_{f_i f_i}\log p(y_i \mid f_i).
\end{equation}

@@

\subsection{Sparse dual Gaussian process} 
\label{sec:sparse-dual-gp}
%
Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation. Many sparsifying approaches exist, we refer the reader to \cite{quinonero2005unifying} for an overview. Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation. We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DITC approximaton \cite{quinonero2005unifying}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$. Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$. As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}. In the paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients. In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.

\begin{equation} 
	\valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
	\vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
\label{eq:dual_sparse}
\end{equation}
Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
\begin{equation}\label{eq:dual_sparse_post}
   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
\end{equation}
where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$. The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$. Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.  Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel. Our approach contrasts to \citet{immerImprovingPredictionsBayesian2021}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset. It is important to highlight that the sparsifying approach is independent of the approximate inference technique. The \cref{eq:dual_param} are determined from the neural network. More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.

\section{Sparse Function-space Sequential Learning}

@@

\subsection{\our for Continual learning}
% Definition of CL -> a sequence of tasks 
In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training. However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model. \todo{this term is replacing the missing data}

% Where the regularizer comes from
At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $m$ inducing points. Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$,\todo{this should be $\kappa(\MX_t, \MX_t)$}, we can exploit the dual parameterization to efficiently encode the information from the $\dataset_t$ using the dual parameterization, as follows, 
\begin{equation}
 	\bar{\MB}^{-1}_t = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, 
 	\quad 
 	\vbeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 	% \quad \forall t \in [1, T]
 \end{equation}
 where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$.

We can then keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs over them computed with the MAP estimate after task $t$, $\vw_t^*$. Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\vw_t^*}(\vz_i)\in \R$. Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.

After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s \in \left[ 1, t-1 \right]$. The resulting regularizer can be computed as follows
\begin{equation}
	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
\end{equation}

\begin{equation}
	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} 
	\left\lVert 
	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
	\right\rVert_{\bar{\MB}^{-1}_{s}}.
\end{equation}
\todo{choose one option}
% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.

%\begin{equation}
%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
%\end{equation}
Then, when the training on the successive task, the new objective to minimize takes the following form
\begin{equation}
	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights, \mathcal{M})
\end{equation}

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/img_super.tex}
\end{table}

Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks. After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}. We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.

@@

\section{Discussion and Conclusion}
\label{sec:conclusion}

@@

\phantomsection%
\addcontentsline{toc}{section}{References}
\begingroup
\small
\bibliographystyle{abbrvnat}
\bibliography{zotero-library,bibliography}
\endgroup

@@

\section{Method Details}

Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

\section{Model-based Reinforcement Learning}
\label{sec-rl-appendix}
